A Survey of Fuzzing and New Technique for Dynamic Analysis

### 2014-02-24 docs/paper/fsuthesis/thesis-template/paper.tex
small chapter refactoring in paper

\section{Motivation}
TODO US gov't interest via money

\begin{lstlisting}[style=cstyle]
// hello.c
#include<stdio.h>
int main() {
	int x = 3;
	printf("%d\n", x);
}
\end{lstlisting}

TODO focus on fact that this stands separate from and complementary to symb. exec? Perhaps performance analysis vs. s2e on binaries to show the potential?

Finding exploitable bugs in binaries is a difficult but valuable endeavour. Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions, is one technique used by researchers and analysts. Applications tested for vulnerabilities are often black boxes because source code is unavailable. This piles difficulties onto an already complex problem, which current research attempts to solve or reduce. Among these issues are:
	\begin{itemize}
		\item efficient and thorough dynamic taint analysis
		\item the path explosion problem [U], and
		\item the code coverage problem. 
	\end{itemize}

 Dynamic taint analysis is also difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky. The path explosion problem arises from the nature of assembly languages. Jump instructions, which may make up a decent percentage of machine instructions in programs, each multiply the total number of existing paths in a binary by two. Considering the size of binaries, this quickly leads to an un-tenably large set of possible paths to explore via conventional techniques like symbolic execution. And even if it is possible to explore all paths in a binary, analysts still need sample input which can trigger the vulnerable condition, perhaps proving that the binary is exploitable along the way. Such automated exploit generation is the subject of much research [H, I].

This work aims to reduce the severity of the latter two problems while being wary of the first during implementation. Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], I focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation. This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to determine smarter ways to mutate user input and create new test cases. For instance, in the below example:

@@

%\begin{verbatim}
%figure 1:
%call read
%mov eax, [ebp - val]
%inc eax
%mul eax, 5
%cmp eax, 42
%jnz 0x8BADC0DE
%\end{verbatim}

@@

\chapter{Preliminaries}

@@

Explain white vs. black box. How gray could bleed into black because of DBI. Talk about SAGE.

@@

\section{TODO Fuzzing Web Applications}

@@

%\begin{lstlisting}[caption=Figure BLAH]
\begin{lstlisting}[style=jsstyle]
// Let userInput = "2 + 2"
var str = eval(userInput);

@@

@@

Talk about CMU Mayhem. [H]
AEG [I]

@@

\chapter{Assumptions and Scoping}

@@

\chapter{Implementation}

@@

\section{results}

@@

% Was setbacks, modify and remove heavily

>>>>

\chapter{Abstract}

Finding exploitable bugs in binaries is a difficult but valuable endeavour. Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions, is one technique used by researchers and analysts. Because many project's source code is not made unavailable to protect intellectual property, applications tested for vulnerabilities are often considered black boxes. Reasoning about the inner working of a complex application when one can only observe the relationship between input and output is hard. In fact, for some situations, like properly implemented cryptography, it is provably hard. This piles difficulties onto an already complex problem, which current research attempts to solve or reduce. Among these issues this paper focuses on:
	\begin{itemize}
		\item efficient and thorough dynamic taint analysis
		\item the path explosion problem [U], and
		\item the code coverage problem. 
	\end{itemize}

 Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky. The path explosion problem arises from the nature of assembly languages. Jump instructions, which may make up a decent percentage of machine instructions in programs, each multiply the total number of existing paths in a binary by two. Considering the size of binaries, this quickly leads to an un-tenably large set of possible paths to explore via conventional techniques like symbolic execution. And even if it is possible to explore all paths in a binary, analysts still need sample input which can trigger the vulnerable condition, perhaps proving that the binary is exploitable along the way. Such automated exploit generation is the subject of much research [H, I].

This work aims to reduce the severity of the latter two problems while being wary of the first during implementation. Chapter 2 explains ZZZZ, Chapter 3 AAAA etc....

Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], I focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation. This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to determine smarter ways to mutate user input and create new test cases. For instance, in the below example:

@@

@@

\section{Motivation}
TODO US gov't interest via money, security issues, etc.

\section{Problem Statement}

TODO Overview of difficulties of fuzzing

\section{State of the Field}

TODO current capabilities and shortcomings of fuzzers

\section{Contributions}

TODO a few paragraphs about what I did, missteps, conclusions, etc.

\chapter{Fuzzing by Example}

TODO fuzzing is a large field, hope to show "fuzzing" by detailing practical examples. Techniques chapter explains a more theoretical base.

@@

TODO Explain white vs. black box. How gray could bleed into black because of DBI. Talk about SAGE.

@@

\section{Fuzzing Web Applications}

@@

\begin{lstlisting}[style=jsstyle]
// Let userInput = "2 + 2"
var str = eval(userInput);

@@

TODO should this section be moved from prelims elsewhere?

@@

TODO AEG [I]?

@@

@@

\chapter{Contribution}

\section{Assumptions and Scoping}

\section{Implementation}

@@

\section{Results}

@@

\section{Lessons Learned}
